---
title: "Homework5"
output: html_document
---

```{r}
library(haven)
library(tidyverse)
library(sandwich)
library(lmtest)
library(plm) 
library(AER)
library(stargazer)
load('FishMarket.RData')
dta1 <- dta
load('Growth_and_democracy.RData')
dta2 <- dta
`?`
#porblem4
(b)
The intercept means when price = 0, the qty will be 8.4.
The b1 = -0.54 means when price is increased by 1, the qty will be decreased by 0.54.
The analysis is not that usefull allthough it has the expect sign of b1 which is negative, there ?hould be many other factors may influence this analysis and causes bias. The intercept also has problem since price will never be zero. 
```{r}
reg1 <- lm(qty~ price,dta1)
coeftest(reg1, vcov = vcovHC(reg1, type = "HC1"))
```

(c)
Both the first and second?stage result is significant. It means that Stormy is a good instrument for price. 
```{r}
reg2_1 <- lm(price~stormy,dta1)
coeftest(reg2_1, vcov = vcovHC, type = "HC1")

reg2_pre <- reg2_1$fitted.values

reg2_2 <- lm(qty~reg2_pre,dta1)
coeftest(reg2_2, vcov?= vcovHC, type = "HC1")
```
(d)Both the first and second stages are significant for the intercept and stormy. While the |t| value for rainy, cold, and days are smaller than 1.96. The coefficient for stormy is a liitle lower than in part (c).
```{r}
reg3_1 ?- lm(price~stormy+rainy+cold+day1+day2+day3+day4,dta1)
coeftest(reg3_1, vcov = vcovHC, type = "HC1")

reg3_pre <- reg3_1$fitted.values

reg3_2 <- lm(qty~reg3_pre+rainy+cold+day1+day2+day3+day4,dta1)
coeftest(reg3_2, vcov = vcovHC, type = "HC1")

reg3_3 <- ?vreg(qty~price+rainy+cold+day1+day2+day3+day4 | stormy+rainy+cold+day1+day2+day3+day4,data = dta1)
coeftest(reg3_3, vcov = vcovHC, type = "HC1")

```
#problem 5
(a)
The intercept means when the log_gdp for the previous year is 0, yje democracy will be -1.3?.
The b1=0.23 means the log_gdp for the previous year is increased by 1, the democracy will be increased by 0.23.
And they are both significant. This model might conclude that higher income lead to more democracy.
```{r}
reg4_1 <- lm(democracy_fh~lag_log_g?p,dta2)
coeftest(reg4_1, vcov = vcovHC, type = "HC1")
```
(b)The model make the regression between democracy and lag_log_gdp while keep the year and country fixed. 
  The coefficient of lad_log_gdp is sigificantly lower than it in (a). The t value is extre?uly smaller than before. 
```{r}
reg5_1 <- plm(democracy_fh~lag_log_gdp+factor(year),dta2,index=c('CountryCode','year'),model='within')
coeftest(reg5_1, vcov = vcovHC(reg5_1, type = "HC1", cluster = 'group'))
```
(c)
It need to satisfy that the woldincome ?hould relate to GDP but not related to democracy. 
(d)
The coefficient of intercept is larger while coefficient of lag_log_gdp is smaller than them in (b).
The standard errir us also larger than before.   
```{r}
dta2$lag_worldincome = rep(NA,length(dta2$w?rldincome))
for(i in 2:length(dta2$worldincome)){
  dta2$lag_worldincome[i] = dta2$worldincome[i-1]
}
reg6_1 <- ivreg(democracy_fh~lag_log_gdp+factor(year)+factor(CountryCode) | lag_worldincome+factor(year)+factor(CountryCode),data = dta2)
coeftest(reg6_1,?vcov = vcovHC, type = "HC1", cluster = 'group')
```



