---
title: "Homwork 4"
output: html_document
---

```{r setup, include=FALSE}
library(haven)
library(tidyverse)
library(sandwich)
library(lmtest)
library(plm)
df = read_dta('Cellphone_panel.dta')
```
(a)
The intercept means when cell_ban and text_ban equal to 0, the deaths will be 13.3808 per billion miles.
b1 = -2.8386 means when there is one more cell ban, the death will be decreased by 2.8386 per biilion miles.
b2 = -2.0616 means when there is one more text ban, the death will be decreased by 2.0616 per biilion miles.
```{r}
reg1 <- lm(DeathsPerBillionMiles~ cell_ban+text_ban,df)
coeftest(reg1, vcov = vcovHC(reg1, type = "HC1"))
```
(b)
The quality of roads in the state.
The states have bad quality of roads will tend to have higher death rate while states have better quality will tend to have lower death rate. And the raod quality is nearly not changes over time. 
This variable should make |b1| and |b2| bigger.
(c)
yes they change as what I expected in (b)
```{r}
reg2 <- plm(DeathsPerBillionMiles~cell_ban+text_ban,df,index=c('state','year'),model='within')
coeftest(reg2, vcov = vcovHC(reg2, type = "HC1", cluster = 'group'))
```
(d)
The national telephone bill from operators like At&t. They give the same price all over the nation but different for each year. 
This variable might lower the coefficients in front of cell_ban and text_ban.
(e)
Yes they change as what I expected in (d)
```{r}
reg3 <- plm(DeathsPerBillionMiles~cell_ban+text_ban+factor(year),df,index=c('state','year'),model='within')
coeftest(reg3, vcov = vcovHC(reg3, type = "HC1", cluster = 'group'))
```
(f)
The coefficient in front of cell_ban and text_ban become a little smaller.
```{r}
reg4 <- plm(DeathsPerBillionMiles~cell_ban+text_ban+urban_percent+cell_per10thous_pop+factor(year),df,index=c('state','year'),model='within')
coeftest(reg4, vcov = vcovHC(reg4, type = "HC1", cluster = 'group'))
```
(g)
Massachusetts has large negative fixed effect and Montana has large positive fixed effect. 
This mean that MA has large negative effect on the result which not changes over time but different across states.
While Montana has large postive effect one the result which not changes over time but different across states.
I can see these difference since there are some factors are state fixed like what I mentioned in part(b).
```{r}
reg5 <- lm(DeathsPerBillionMiles~cell_ban+text_ban+urban_percent+cell_per10thous_pop+factor(year)+factor(state),df)
summary(reg5)
coeftest(reg4, vcov = vcovHC(reg4, type = "HC1", cluster = 'group'))
fixef(reg4)
```

